
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet = TRUE)
current_date <- Sys.Date()
```
---
title: "Summary of GLM runs"
output: html_document
date: `r current_date`
---

### NLDAS runs
``` {r, echo = FALSE}
tar_load(p1_nldas_site_ids)
tar_load(p1_lake_to_state_xwalk_df)
tar_load(p2_nldas_glm_uncalibrated_runs)
tar_load(p2_nldas_glm_uncalibrated_run_groups)
tar_load(p3_nldas_glm_uncalibrated_output_feather_tibble)
tar_load(p1_nldas_dates)

nldas_timeperiod <- sprintf('%s to %s', p1_nldas_dates$driver_start_date, p1_nldas_dates$driver_end_date)
nldas_run_summary <- p3_nldas_glm_uncalibrated_output_feather_tibble %>%
  group_by(state) %>%
  summarize(n_lakes = length(unique(site_id)), .groups='keep')
```

Using `r unique(p2_nldas_glm_uncalibrated_runs$driver)` driver data and GLM version `r unique(p2_nldas_glm_uncalibrated_runs$glm_version)`, we modeled `r length(p1_nldas_site_ids)` lakes across `r length(unique(p1_lake_to_state_xwalk_df$state))` states (`r unique(p1_lake_to_state_xwalk_df$state)`). For each lake, we modeled lake temperatures from `r nldas_timeperiod`. Models ran successfully for `r length(unique(p2_nldas_glm_uncalibrated_run_groups$site_id))` lakes.

``` {r nldas_run_summary, echo = FALSE, results = 'asis'}
library(knitr)
kable(nldas_run_summary, caption = "Summary of successful NLDAS runs")
```

### GCM runs

```{r, echo=FALSE}
tar_load(p1_gcm_site_ids)
tar_load(p1_lake_cell_tile_xwalk_df)
tar_load(p2_gcm_glm_uncalibrated_runs)
tar_load(p2_gcm_glm_uncalibrated_run_groups)
tar_load(p3_gcm_glm_uncalibrated_output_feather_tibble)
tar_load(p1_gcm_dates)

gcm_timeperiod_1 <- sprintf('%s to %s', p1_gcm_dates$driver_start_date[1], p1_gcm_dates$driver_end_date[1])
gcm_timeperiod_2 <- sprintf('%s to %s', p1_gcm_dates$driver_start_date[2], p1_gcm_dates$driver_end_date[2])
gcm_timeperiod_3 <- sprintf('%s to %s', p1_gcm_dates$driver_start_date[3], p1_gcm_dates$driver_end_date[3])
gcm_run_summary <- p3_gcm_glm_uncalibrated_output_feather_tibble %>%
  group_by(state) %>%
  summarize(n_lakes = length(unique(site_id)), .groups='keep')
```

Using driver data for `r length(unique(p2_gcm_glm_uncalibrated_runs$driver))` GCMs (`r unique(p2_gcm_glm_uncalibrated_runs$driver)`) and GLM version `r unique(p2_gcm_glm_uncalibrated_runs$glm_version)`, we modeled `r length(p1_gcm_site_ids)` lakes across `r length(unique(p1_lake_cell_tile_xwalk_df$state))` states (`r unique(p1_lake_cell_tile_xwalk_df$state)`). For each lake and each GCM, we modeled lake temperatures during three time periods: `r gcm_timeperiod_1`, `r gcm_timeperiod_2`, and `r gcm_timeperiod_3`. Models for all three time periods for all `r length(unique(p2_gcm_glm_uncalibrated_run_groups$driver))` GCMs ran successfully for `r length(unique(p2_gcm_glm_uncalibrated_run_groups$site_id))` lakes.

``` {r gcm_run_summary, echo = FALSE, results = 'asis'}
kable(gcm_run_summary, caption = "Summary of successful GCM runs")
```